### 2021-01-24 paper/intro.tex
Added paragraph to intro

This paper is the first model of relaxed memory with a compositional
semantics for sequential composition.  It shows how the pomsets with
preconditions model of~\cite{DBLP:journals/pacmpl/JagadeesanJR20} can be combined
with the predicate transformer model of~\cite{DBLP:journals/cacm/Dijkstra75}.
\begin{itemize}
\item \S\ref{sec:model} presents the basic model, with few features
  required of the logic of preconditions, but a resulting lack of fidelity
  to exiting models,
\item \S\ref{sec:q} adds a model of \emph{quiescence} to the logic,
  required to model coherence (accessing $x$ has a precondition that $x$ is quiescent)
  and synchronization (a releasing write requires all locations to be quiescent),
\item \S\ref{sec:arm} adds the features required for efficient compilation
  to modern architectures: downgrading some synchronized accesses to relaxed,
  and removing read-read dependencies,
\item \S\ref{sec:complications} show how to address common litmus tests, and
\item \S\ref{sec:discussion} is a discussion of the design space.
\end{itemize}
% Acknowledgements go here, once we're not double-blinded.

>>>>

This paper is the first model of relaxed memory with a compositional
semantics for sequential composition.  It shows how pomsets with
preconditions~\cite{DBLP:journals/pacmpl/JagadeesanJR20} can be combined
with predicate transformers~\cite{DBLP:journals/cacm/Dijkstra75}.
\begin{itemize}
\item \S\ref{sec:model} presents the basic model, with few features
  required of the logic of preconditions, but a resulting lack of fidelity
  to exiting models,
\item \S\ref{sec:q} adds a model of \emph{quiescence} to the logic,
  required to model coherence (accessing $x$ has a precondition that $x$ is quiescent)
  and synchronization (a releasing write requires all locations to be quiescent),
\item \S\ref{sec:arm} adds the features required for efficient compilation
  to modern architectures: downgrading some synchronized accesses to relaxed,
  and removing read-read dependencies,
\item \S\ref{sec:complications} show how to address common litmus tests, and
\item \S\ref{sec:discussion} is a discussion of the design space.
\end{itemize}
% Acknowledgements go here, once we're not double-blinded.
The definitions in this paper have been formalized in Agda.

Because it is closely related, we expect that the memory-model results of
\cite{DBLP:journals/pacmpl/JagadeesanJR20} apply to our model, including
compositional reasoning for temporal safety properties and {local} \drfsc.
In \textsection\ref{sec:arm}, we provide an alternative proof strategy for
efficient compilation to \armeight{}, which improves upon that of
\cite{DBLP:journals/pacmpl/JagadeesanJR20} by using a recent alternative
characterization of \armeight{}.
